---
output: pdf_document
params:
  prod1: NULL
  prod2: NULL
  prod3: NULL
  prod4: NULL
  prod5: NULL
  prod6: NULL
  prod7: NULL
  prod8: NULL
  prod9: NULL
  inc1: NULL
  inc2: NULL
  inc3: NULL
  inc4: NULL
  inc5: NULL
  inc6: NULL
  inc7: NULL
  inc8: NULL
  inc9: NULL
  linc1: NULL
  linc2: NULL
  linc3: NULL
  linc4: NULL
  linc5: NULL
  linc6: NULL
  linc7: NULL
  linc8: NULL
  linc9: NULL
  totalmult: NULL
  gdpmult: NULL
  labmult: NULL
  capmult: NULL
  poormult: NULL
  nonpoormult: NULL
  sim_TouristSpending: NULL
  sim_PASpending: NULL
  sim_ComRevShSpending: NULL
  sim_AgSpending: NULL
  sim_NagSpending: NULL
  sim_LFUSKSpending: NULL
  sim_LMUSKSpending: NULL
  sim_LFSKSpending: NULL
  sim_LMSKSpending: NULL
---


# PA LEWIE-lite Dashboard: Local-economy impacts of tourist spending

&nbsp;

## For every dollar of tourist spending (multipliers):

Total Production Multiplier:
```{r echo=FALSE, comment=NA}
  cat(params$totalmult())
```

&nbsp;

Accruing to Poor Households:
```{r echo=FALSE, comment=NA}
  cat(params$poormult())
```

&nbsp;

Accruing to Labor:
```{r echo=FALSE, comment=NA}
  cat(params$labmult())
```

&nbsp;

Total Income Multiplier:
```{r echo=FALSE, comment=NA}
  cat(params$gdpmult())
```

&nbsp;

Accruing to NonPoor Households:
```{r echo=FALSE, comment=NA}
  cat(params$nonpoormult())
```

&nbsp;

Accruing to Capital:
```{r echo=FALSE, comment=NA}
  cat(params$capmult())
```

\newpage
## Local economy-wide impact of tourist spending

How much tourist spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_TouristSpending)
```

&nbsp;

```{r echo=FALSE}
  params$prod1()
```

&nbsp;

```{r echo=FALSE}
  params$inc1()
```

&nbsp;

```{r echo=FALSE}
  params$linc1()
```

\newpage
## Local-economy impacts of park spending (US$)

How much park spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_PASpending)

```{r echo=FALSE}
  params$prod2()
```

&nbsp;

```{r echo=FALSE}
  params$inc2()
```

&nbsp;

```{r echo=FALSE}
  params$linc2()
```

\newpage
## Local-economy impacts of community spending (US$)

How much community spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_ComRevShSpending)

```{r echo=FALSE}
  params$prod3()
```

&nbsp;

```{r echo=FALSE}
  params$inc3()
```

&nbsp;

```{r echo=FALSE}
  params$linc3()
```

\newpage
## Local-economy impacts of increased agricultural production (US$)

How much increase in local agricultural production ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_AgSpending)

```{r echo=FALSE}
  params$prod4()
```

&nbsp;

```{r echo=FALSE}
  params$inc4()
```

&nbsp;

```{r echo=FALSE}
  params$linc4()
```

\newpage
## Local-economy impacts of increased Non-Agricultural production (US$)

How much increase in local Non-Agricultural production ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_NagSpending)

```{r echo=FALSE}
  params$prod5()
```

&nbsp;

```{r echo=FALSE}
  params$inc5()
```

&nbsp;

```{r echo=FALSE}
  params$linc5()
```

\newpage
## Local-economy impacts of low-skilled female earnings (US$)

How much increase in earnings of low-skilled female workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LFUSKSpending)

```{r echo=FALSE}
  params$prod6()
```

&nbsp;

```{r echo=FALSE}
  params$inc6()
```

&nbsp;

```{r echo=FALSE}
  params$linc6()
```

\newpage
## Local-economy impacts of low-skilled male earnings (US$)

How much increase in earnings of low-skilled male workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LMUSKSpending)

```{r echo=FALSE}
  params$prod7()
```

&nbsp;

```{r echo=FALSE}
  params$inc7()
```

&nbsp;

```{r echo=FALSE}
  params$linc7()
```

\newpage
## Local-economy impacts of skilled female earnings (US$)

How much increase in earnings of skilled female workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LFSKSpending)

```{r echo=FALSE}
  params$prod8()
```

&nbsp;

```{r echo=FALSE}
  params$inc8()
```

&nbsp;

```{r echo=FALSE}
  params$linc8()
```

\newpage
## Local-economy impacts of skilled male earnings (US$)

How much increase in earnings of skilled male workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LMSKSpending)

```{r echo=FALSE}
  params$prod9()
```

&nbsp;

```{r echo=FALSE}
  params$inc9()
```

&nbsp;

```{r echo=FALSE}
  params$linc9()
```