---
output: pdf_document
params:
  prod1: NULL
  prod2: NULL
  prod3: NULL
  prod4: NULL
  prod5: NULL
  prod6: NULL
  prod7: NULL
  prod8: NULL
  prod9: NULL
  inc1: NULL
  inc2: NULL
  inc3: NULL
  inc4: NULL
  inc5: NULL
  inc6: NULL
  inc7: NULL
  inc8: NULL
  inc9: NULL
  linc1: NULL
  linc2: NULL
  linc3: NULL
  linc4: NULL
  linc5: NULL
  linc6: NULL
  linc7: NULL
  linc8: NULL
  linc9: NULL
  earn1: NULL
  totalmult: NULL
  gdpmult: NULL
  labmult: NULL
  capmult: NULL
  poormult: NULL
  nonpoormult: NULL
  sim_TouristSpending: NULL
  sim_PASpending: NULL
  sim_ComRevShSpending: NULL
  sim_AgSpending: NULL
  sim_NagSpending: NULL
  sim_LFUSKSpending: NULL
  sim_LMUSKSpending: NULL
  sim_LFSKSpending: NULL
  sim_LMSKSpending: NULL
---


# PA LEWIE-lite: Local-Economy Impacts of Tourist Spending

&nbsp;

## For every dollar of tourist spending (multipliers):

Total Production Multiplier:
```{r echo=FALSE, comment=NA}
  cat(params$totalmult())
```

&nbsp;

Accruing to Poor Households:
```{r echo=FALSE, comment=NA}
  cat(params$poormult())
```

&nbsp;

Accruing to Labor:
```{r echo=FALSE, comment=NA}
  cat(params$labmult())
```

&nbsp;

Total Income Multiplier:
```{r echo=FALSE, comment=NA}
  cat(params$gdpmult())
```

&nbsp;

Accruing to NonPoor Households:
```{r echo=FALSE, comment=NA}
  cat(params$nonpoormult())
```

&nbsp;

Accruing to Capital:
```{r echo=FALSE, comment=NA}
  cat(params$capmult())
```

\newpage
## Local-economy Impacts of Tourist Spending (US$)

How much tourist spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_TouristSpending)
```

&nbsp;

### EFFECTS OF THIS TOURISM SPENDING ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod1()
  params$inc1()
```
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$linc1()
  params$earn1()
```

\newpage
## Local-economy Impacts of Park Spending (US$)

How much park spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_PASpending)
```

&nbsp;

### EFFECTS OF THIS PARK BUDGET ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod2()
  params$inc2()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc2()
```

\newpage
## Local-economy Impacts of Community Spending (US$)

How much community spending ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_ComRevShSpending)
```

&nbsp;

### EFFECTS OF THIS COMMUNITY SPENDING ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod3()
  params$inc3()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc3()
```

\newpage
## Local-economy Impacts of Increased Agricultural Production (US$)

How much increase in local agricultural production ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_AgSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN LOCAL AGRICULTURAL PRODUCTION ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod4()
  params$inc4()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc4()
```

\newpage
## Local-economy Impacts of Increased Non-Agricultural Production (US$)

How much increase in local Non-Agricultural production ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_NagSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN LOCAL NON-AGRICULTURAL PRODUCTION ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod5()
  params$inc5()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc5()
```

\newpage
## Local-economy Impacts of Low-Skilled Female Earnings (US$)

How much increase in earnings of low-skilled female workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LFUSKSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN EARNINGS TO LOW SKILLED FEMALE WORKERS ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod6()
  params$inc6()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc6()
```

\newpage
## Local-economy Impacts of Low-Skilled Male Earnings (US$)

How much increase in earnings of low-skilled male workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LMUSKSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN EARNINGS TO LOW SKILLED MALE WORKERS ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod7()
  params$inc7()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc7()
```

\newpage
## Local-economy Impacts of Skilled Female Earnings (US$)

How much increase in earnings of skilled female workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LFSKSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN EARNINGS TO SKILLED FEMALE WORKERS ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod8()
  params$inc8()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc8()
```

\newpage
## Local-economy Impacts of Skilled Male Earnings (US$)

How much increase in earnings of skilled male workers ($) do you expect?
```{r echo=FALSE, comment=NA}
  cat(params$sim_LMSKSpending)
```

&nbsp;

### EFFECTS OF THIS INCREASE IN EARNINGS TO SKILLED MALE WORKERS ON...
```{r echo=FALSE, out.width="50%", fig.align="default"}
  params$prod9()
  params$inc9()
```
```{r echo=FALSE, out.width="50%", fig.align="center"}
  params$linc9()
```