---
output: pdf_document
params:
  totalmult: NULL
  gdpmult: NULL
  labmult: NULL
  capmult: NULL
  poormult: NULL
  nonpoormult: NULL
  touractmult: NULL
  nontouractmult: NULL
  park_name: NULL
  numtour: NULL
  numtourSingle: NULL
  numtourMulti: NULL
  avgTouristLength: NULL
  avgTouristSpending: NULL
  entryFee: NULL
  totalEntryFees: NULL
  budget: NULL
  parkWageBill: NULL
---

\begin{center}
\section{LEWIE-lite Dashboard Report}
\end{center}

&nbsp;

\subsection{Overview of tourism in the park}

&nbsp;

Park name:
```{r echo=FALSE, comment=NA}
	cat(params$park_name())
```

&nbsp;

```{r echo=FALSE, comment=NA, fig.align="center", warning = FALSE, message = FALSE}
library(ggplot2)
library(emojifont)
library(fontawesome)
## Only fontawesome 4 icons supported

rows <- 3
cols <- 3
boxes <- 9
padding <- 1
h <- 14
w <- 22
icons<-c("fa-dollar", "fa-file-text", "fa-briefcase", "fa-calendar", "fa-money", "fa-ticket", "fa-male", "fa-sun-o", "fa-bed")

df <- data.frame(
    x = rep(seq(0, (w+padding)*cols-1, w+padding), times=rows),
    y = rep(seq(0, (h+padding)*rows-1, h+padding), each=cols),
    h = rep(h, boxes),
    w = rep(w, boxes),
    value = c(params$totalEntryFees(), params$budget(), params$parkWageBill(), params$avgTouristLength(), params$avgTouristSpending(), params$entryFee(), params$numtour(), params$numtourSingle(), params$numtourMulti()),
    info = c("Total Entry Fees",
             "Total Park Budget",
             "Park Spending on Local Wages",
             "Average Length of Stay",
             "Average Tourist Spending",
             "Park Entry Fee (average)",
             "Total Number of Tourists",
             "Single-day Tourists",
             "Multi-day Tourists"),
    icon = fontawesome(icons),
    font_family = c(rep("fontawesome-webfont", boxes)),
    color = factor(1:boxes)
)

ggplot(df, aes(x, y, height = h, width = w, label = info)) +
    ## Create the tiles using the `color` column
    geom_tile(aes(fill = color)) +
    ## Add the numeric values as text in `value` column
    geom_text(color = "white", fontface = "bold", size = 8,
              aes(label = value, x = x - w/2.2, y = y + h/4), hjust = 0) +
    ## Add the labels for each box stored in the `info` column
    geom_text(color = "white", fontface = "bold", size = 3,
              aes(label = info, x = x - w/2.2, y = y-h/4), hjust = 0) +
    coord_fixed() +
    scale_fill_brewer(type = "qual", palette = "Dark2", direction=-1, na.value = "dodgerblue4") +
    ## Use `geom_text()` to add the icons by specifying the unicode symbol.
    geom_text(size = 16, aes(label = icon, family = font_family,
                             x = x + w/4, y = y + h/8), alpha = 0.25) +
    theme_void() +
    guides(fill = FALSE)
```

\newpage
\subsection{Local-economy impacts of tourist spending (US\$)}

&nbsp;

### For every dollar of tourist spending, the total production multiplier is:

&nbsp;

```{r echo=FALSE, comment=NA, fig.align="center", warning = FALSE, message = FALSE}
rows <- 2
cols <- 2
boxes <- 4
padding <- 0.25
h <- 2
w <- 6
icons<-c("fa-sun-o", "fa-briefcase", "fa-gears", "")

df <- data.frame(
    x = rep(seq(0, (w+padding)*cols-1, w+padding), times=rows),
    y = rep(seq(0, (h+padding)*rows-1, h+padding), each=cols),
    h = rep(h, boxes),
    w = rep(w, boxes),
    value = c(params$touractmult(), params$nontouractmult(), params$totalmult(), ""),
    info = c("Tourism activities",
             "Non-Tourism activities",
             "Total Production Multiplier", "Which can be split into:"),
    icon = fontawesome(icons),
    font_family = c(rep("fontawesome-webfont", boxes)),
    color = factor(1:boxes)
)

ggplot(df, aes(x, y, height = h, width = w, label = info)) +
    ## Create the tiles using the `color` column
    geom_tile(aes(fill = color)) +
    ## Add the numeric values as text in `value` column
    geom_text(color = "white", fontface = "bold", size = 8,
              aes(label = value, x = x - w/2.2, y = y + h/4), hjust = 0) +
    ## Add the labels for each box stored in the `info` column
    geom_text(color = "white", fontface = "bold", size = 3,
              aes(label = info, x = x - w/2.2, y = y-h/4), hjust = 0) +
    coord_fixed() +
    scale_fill_brewer(type = "qual", palette = "Dark2") +
    ## Use `geom_text()` to add the icons by specifying the unicode symbol.
    geom_text(size = 16, aes(label = icon, family = font_family,
                             x = x + w/4, y = y + h/8), alpha = 0.25) +
    theme_void() +
    guides(fill = FALSE)
```

&nbsp;

The production multiplier represents the total value of goods and services generated in the economy for every dollar spent by a tourist, including all higher-order impacts, or ripple effects (e.g.: Tourist spends money at a restaurant, the cook spends some of those wages at a local shop, the shopkeeper spends some of those profits buying food from a farmer, etc.)

\newpage
### For every dollar of tourist spending, the total income multiplier is:

&nbsp;

```{r echo=FALSE, comment=NA, fig.align="center", warning = FALSE, message = FALSE}
rows <- 2
cols <- 2
boxes <- 4
padding <- 0.25
h <- 2
w <- 6
icons<-c("fa-user", "fa-building", "fa-line-chart", "")

df <- data.frame(
    x = rep(seq(0, (w+padding)*cols-1, w+padding), times=rows),
    y = rep(seq(0, (h+padding)*rows-1, h+padding), each=cols),
    h = rep(h, boxes),
    w = rep(w, boxes),
    value = c(params$labmult(), params$capmult(), params$gdpmult(), ""),
    info = c("Accruing to Labor",
             "Accruing to Capital",
             "Total Income Multiplier", "Which can be split into:"),
    icon = fontawesome(icons),
    font_family = c(rep("fontawesome-webfont", boxes)),
    color = factor(1:boxes)
)

ggplot(df, aes(x, y, height = h, width = w, label = info)) +
    ## Create the tiles using the `color` column
    geom_tile(aes(fill = color)) +
    ## Add the numeric values as text in `value` column
    geom_text(color = "white", fontface = "bold", size = 8,
              aes(label = value, x = x - w/2.2, y = y + h/4), hjust = 0) +
    ## Add the labels for each box stored in the `info` column
    geom_text(color = "white", fontface = "bold", size = 3,
              aes(label = info, x = x - w/2.2, y = y-h/4), hjust = 0) +
    coord_fixed() +
    scale_fill_brewer(type = "qual", palette = "Set1", direction=-1) +
    ## Use `geom_text()` to add the icons by specifying the unicode symbol.
    geom_text(size = 16, aes(label = icon, family = font_family,
                             x = x + w/4, y = y + h/8), alpha = 0.25) +
    theme_void() +
    guides(fill = FALSE)
```

&nbsp;

### Alternatively, the income multiplier can also be split based on household income:

&nbsp;

```{r echo=FALSE, comment=NA, fig.align="center", warning = FALSE, message = FALSE}
rows <- 2
cols <- 2
boxes <- 4
padding <- 0.25
h <- 2
w <- 6
icons<-c("fa-money", "fa-money", "fa-line-chart", "")

df <- data.frame(
    x = rep(seq(0, (w+padding)*cols-1, w+padding), times=rows),
    y = rep(seq(0, (h+padding)*rows-1, h+padding), each=cols),
    h = rep(h, boxes),
    w = rep(w, boxes),
    value = c(params$poormult(), params$nonpoormult(), params$gdpmult(), ""),
    info = c("Accruing to Poor Households",
             "Accruing to NonPoor Households",
             "Total Income Multiplier", "Alternatively, can be split into:"),
    icon = fontawesome(icons),
    font_family = c(rep("fontawesome-webfont", boxes)),
    color = factor(1:boxes)
)

ggplot(df, aes(x, y, height = h, width = w, label = info)) +
    ## Create the tiles using the `color` column
    geom_tile(aes(fill = color)) +
    ## Add the numeric values as text in `value` column
    geom_text(color = "white", fontface = "bold", size = 8,
              aes(label = value, x = x - w/2.2, y = y + h/4), hjust = 0) +
    ## Add the labels for each box stored in the `info` column
    geom_text(color = "white", fontface = "bold", size = 3,
              aes(label = info, x = x - w/2.2, y = y-h/4), hjust = 0) +
    coord_fixed() +
    scale_fill_brewer(type = "qual", palette = "Set1", direction=-1) +
    ## Use `geom_text()` to add the icons by specifying the unicode symbol.
    geom_text(size = 16, aes(label = icon, family = font_family,
                             x = x + w/4, y = y + h/8), alpha = 0.25) +
    theme_void() +
    guides(fill = FALSE)
```

&nbsp;

The income multiplier represents the total value of incomes that are generated in the economy for every dollar spent by a tourist, including all ripple effects (income of the cook, and of the shopkeeper, and of the farmer, etc). The income multiplier is always smaller than the production multiplier, because it is a subset of it (like profits are a subset of revenue).